---
title: "Weight of Fish"
author: "Alex Moreno"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight


## Perch

```{r}
pwt = lm(Weight~ Length1+ Length2 + Length3 + Height, data = Perch)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```
```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```




### Best Models

The best model is using all 4 variables. 

### Best Two regressor model

From the table shown, the best two-parameter regressor model is based on Length3 and Height


## Pike

```{r}
pwt = lm(Weight~ Length1+ Length2 + Length3 + Height, data = Pike)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```
```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


### Best Models

The best model is using all 4 variables.


### Best Two regressor model

From the table shown, the best two-parameter regressor model is based on Length1 & Length3. 


## Roach

```{r}
pwt = lm(Weight~ Length1+ Length2 + Length3 + Height, data = Roach)
summary(pwt)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```
```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

The best model is using all 4 variables.

### Best Two regressor model

From the graph the best two-parameter regressor model is based on Length1 & Length3.


## Final Summary Statements

From the analysis we made, the best models for all 3 fish; Pike, Perch, and Roach; is using all 4 variables. The best two regressor model variables for Perch is Length3 & Height. The best two regressor model variables for Pike is Length1 & Length3. The best two regressor model variables for Roach is Length1 & Length3.

